Toxic Code Snippets on Stack Overflow

### 2018-05-24 cloverflow-tse/cover_letter/cover_letter.tex
Incorporated Jens's comments on the cover letter.

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software
Engineering. This is a re-submission of the previous submission
no.~TSE-2017-11-0335 and we would like to thank the anonymous Reviewers for
taking their time to carefully read our paper. With their useful and
constructive reviews, we substantially improved the work by adding three major
improvements as listed below to our previous submission and minor improvements
as discussed later in this letter:

\textbf{1. A study of toxic code snippets on GitHub:}~To provide an evidence
that toxic code snippets are actually reused in software projects and strengthen
the motivation, we performed a large-scale analysis of clones between the
discovered online code clones, 100 outdated and 214 license-incompatible code snippets, 
on Stack Overflow and 130,703 GitHub projects using a clone detection tool followed by manual validation.

\textbf{2. Analysis of the tools' parameter settings:}~We mitigated the threats to
validity due to parameter settings of the clone detection tools and the clone
merging technique by exploring different tools' parameter values.

\textbf{3. Extended analysis of online code clones:}~We performed an extended analyses
on the 2,289 online code clones and 100 outdated code snippets. For example,
we analysed the size and age of the clones, and summarised the six intents that
made the clones outdated.

\textbf{4. Revisions to the overall discussion:}~We substantially expanded the
overall discussion to include (1) a discussion of toxicity of outdated and
license-incompatible clones on Stack Overflow and their implications, and (2) more detailed discussion
of how to implement the tools or approaches proposed in the preventive and
detective measures, and (3) a suggestion for automation of code cloning direction detection.

We also tried our best to address all the comments from the reviewers. Every
comment led to an improvement(s) on this submission and we discuss them in order as shown in the
next sections.

@@

\begin{enumerate}
	\item We understand the concern of finding real evidence to support the claim that code snippets on Stack Overflow do appear in open- or closed-source software projects. Hence, we have performed a study of code clone detection between our 100 reported outdated code snippets on Stack Overflow and 131,703 GitHub projects. We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not. We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them. As shown in Table~\ref{tab:outdated_github} below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub. For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).

@@

	Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks). Due to the lack of evidence, we could not conclude how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects. It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.  
	Nevertheless, we reported the developers of the two projects regarding the issue. We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop. The issue has been fixed in deeplearning4j. The developers of deeplearning4j agreed that the method was problematic and decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base. On the other hand, the bug report in Apache Hive is still unfixed.

	\item The same study has been done for another type of toxic code snippets on Stack Overflow, license-incompatible code snippets. 
	We detected clones between the 214
	code snippets without their original license (86 QS, 78 EX and 50 UD)  and
	130,703 GitHub projects using SourcererCC with 80\% similarity threshold. 
	Opposite to the outdated clones, we discovered many more clones
	of 7,207 candidate pairs.
	Then, we used the Ninka tool to automatically identify software license from the 7,207
	code snippets.  There were 90 pairs from 10 Qualitas projects on
	GitHub and 7,117 pairs from 2,427 other projects. From
	Table \ref{tab:license_github} below, the clones were found from highly-starred
	projects (29,465 to 10 stars) to 1-star projects.
	We found 12 code snippets with attributions to Stack Overflow questions/answers and
	6 of them were the answers we found as clones from Qualitas or external sources.
	Five code snippets did not have license while the originals had Apache-2, GPLv2,
	or EPLv1 license. One snippets had AGPLv3 license while the original had Apache-2 license.
	Only 995 code snippets in GitHub projects that have the same license
	as the originals in Qualitas.

@@

	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub. However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information. Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
	We also updated the Overall Discussion section to reflect the findings that (1) there is only a small number of toxic code snippets from outdated code that are found in GitHub projects, (2) there is a large number of toxic code snippets caused by missing license that are found in GitHub projects. %Moreover, the direction of copying is also unclear. The clones could come from Stack Overflow, the original project repositories, or other places. 
\end{enumerate}

@@

We partially address this comment in the previous answer by performing an empirical study of code cloning between Stack Overflow toxic code snippets and GitHub projects. Furthermore, we also improved the paper on the aspect of the awareness of information-seekers to toxic code snippets on Stack Overflow by including the results from another survey of Stack Overflow visitors (i.e.~information seekers). This survey of the Stack Overflow visitors was performed during the same time as the Stack Overflow answerers (25 July 2017 to 25 September 2017) and the full results are reported in our technical report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the previous version of the paper due to a smaller sample size compared to the answerers survey. However, we did find some interesting results so we have included them into this version and discussed the key findings in~RQ1. The brief summary of the visitor survey is as follows.

@@

We surveyed 87 Stack Overflow visitors (visit the site and reuse code from Stack Overflow at least once) via five channels: social media post (Facebook),
\textsf{blognone.com}, a popular IT community and discussion forum in Thailand, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering
Facebook page.

The visitors survey confirms the findings from the previous studies that Stack
Overflow code snippets can be problematic~\citep{Zhang2018,Acar2016,An2017}. Sixty-six
percent of the visitors experienced a problem from reusing Stack Overflow code
snippets ranging from incorrect solutions, outdated solutions, mismatched
solutions, to buggy code. Although they are aware of the problems, half of them
(56\%) never reports back to the Stack Overflow discussions. On the other hand,
the visitors rarely give attributions to Stack Overflow when they reuse code
snippets from the website, similar to the findings reported
by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
license, and more than half of them never check for license compatibility when
reusing Stack Overflow code snippets. 
Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
check if the code snippet originated from a different source (e.g. an open source project) 
and if they had an incompatible license to their projects.
Moreover, we also found that 9\% of the participants
encountered legal issues by copying code from Stack Overflow. To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

@@

\begin{enumerate}
	\item We added a discussion of toxicity of outdated and license-incompatible clones on Stack Overflow. Although we found some harmful outdated clones, we could not find evidence that they are widely reused in open source projects on GitHub. Therefore, the damage is not high since there is only a few outdated code snippets that are harmful for reuse. On the other hand, the problem of license incompatibility caused by missing original license in Stack Overflow code snippets can cause more damage than outdated code. Different legal system and different interpretation of fair-use concept and de minimis (i.e.~the minimal lines of code allowed to be copied without violating copyright) in each country can make a reuse of these code snippets becoming illegal.

@@

	\item To address your point about auditing platforms/services, 
	we performed a study of two open source software auditing
	platforms/services:~BlackDuck
	Software\footnote{https://www.blackducksoftware.com} and
	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from their
	report~\cite{CORSI2017} that while they check for code copied from open source
	projects including GitHub and Stack Overflow and analyse their license
	compatibility with their customer software, the BlackDuck auditing system will
	treat the code snippets on Stack Overflow as having ``unknown'' license because
	it does not know the original license of Stack Overflow code snippets. For nexB,
	their product does not mention checking of reused source code from Stack
	Overflow. So, our proposed preventive measure, which can offer more precise licensing
	information of Stack Overflow code snippets, will be useful as an add-on license
	check for code copying from Stack Overflow. We include this in the Overall Discussion.
\end{enumerate}

@@

You are right. We mainly study the online code clones and established their existence. However, we used the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning. 
Moreover, the term code cloning is not well known outside the code cloning community. Code clones are called differently in each research community or in practice, such as duplicated code, copy-and-paste code, code reuse, software similarity or software redundancy. So, we decided not to use the term in the title.

@@

``Although this activity of online code cloning is well-known, there is only a few
empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017}, especially
the on finding the origins of the clones.
We tackle this challenge of establishing existence of online code clones and
investigate how they occur in this study.''
%Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.

@@

That is a fair point and we would like to analyse the statistics as you suggested. 
To answer your question in (a), the number of views
is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).
For (b), unfortunately, for our experiment we extracted only the code snippets from the Stack Overflow dumps but not other information. They are the only available data of the January 2016 snapshot we currently have. We checked and found that the latest available Stack Overflow dump already contains different data than the one we used in our study since it is now more than 2 years newer, and will result in incorrect statistics and inconsistent results.
For (c), that is a really interesting idea. However, it is out of the scope of this study and would involve an extensive analysis of the data so we may investigate it in the future work.

@@

Thank you for the detailed checking of the Stack Overflow post. Interestingly, this is surprising to us as well. The comment in the post 22262310 by Joseph K on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare} method is actually from a student in our class. His name is Joseph Kalash and he is a master student in Machine Learning MsC program at UCL Computer Science department \footnote{Joseph's CV can be found here: \url{https://jkala.sh/cv}}. We assigned a preprint of this paper to students in the COMPGS11 -- Research Seminar in Software Engineering course and had a discussion about the paper on Thu 2 November 2017. Joseph, who was an active Stack Overflow member, was one of the students in the class and he actively participated in the discussion. It seemed like he had seen the Hadoop's toxic code snippet in the paper and decided to post a comment to warn other users.

Nevertheless, since this is a very interesting suggestion. We also performed an investigation of the 100 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet. We include the result of this investigation in the RQ4. We found that, out of 100 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment). Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data. None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users. We added this discussion in the RQ4.

@@

We appreciate the comments. We have refined our definition of toxic code snippets in the paper by adapting from Israel Gat's definition~\citep{toxiccode} which links toxic code to technical debt, i.e.~``a metaphor reflecting technical compromises that can yield short-term benefit but may hurt the long-term health of a software system''~\citep{Li2015}. The new definition of toxic doe snippets are as follows.

@@

Stack Overflow allows its users to edit their own posts, i.e.~questions/answers~\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts~\footnote{https://stackoverflow.com/help/privileges/edit}. Thus, if the code snippet in an answer is outdated and has an issue, the answerer or other high-reputation users can update the answer to be up-to-date or to warn other users that the code is already outdated and may contain problems. We found some discussions regarding this concern on Metaexchange as well so the Stack Overflow community is also considering this option~\footnote{Discussion about outdated answer: https://meta.stackexchange.com/questions/131495/how-to-handle-outdated-answers and https://meta.stackexchange.com/questions/180864/editing-outdated-source-code-in-an-answer}. We included this discussion in the paper.

Based on your suggestion of looking at other newer or higher-voted answers, we performed an investigation of all the answers in 100 posts containing outdated code snippets as accepted answers. We found that there were 34 posts which contains newer answers. Regarding the number of votes, there were 5 posts which contained other answers with a higher number of votes than the outdated answer. Ninety-nine out of the one hundred outdated code were still marked as accepted answers. 
This discussion of the findings is added to the the RQ4.

@@

Good point. Although we grouped the code modifications that make Stack Overflow snippets outdated into 6 categories as shown in Table 9, we did not investigate the motivation of the changes such as code refactoring or variable renaming. We have performed the check as you suggested by checking the commit message of each change that make the code outdated. The findings are discussed below and are included in the RQ4.

@@

The majority, 64, of the changes are due to code enhancement, such as adding a new features or improving existing code to support a newer version of the language or APIs. Fifteen changes are for removal of dead or deprecated code such as SQL connection code example in Hibernate. Ten changes are made to fix bugs in the software (e.g.~array reference, race condition, wrong field access, \texttt{NullPointerException}). There are 6 changes for code refactoring, 3 changes for updating coding styles using an automated tool or manually, and 2 changes that are caused by the change of data format.

@@

We used the Stack Overflow data dump of January 2016 since it was the latest dump when we started our experiment. Nonetheless, we finally completed the whole experiment, the result analysis, and the survey two years later. That is why the dump is 2 years old.

@@

%Choosing this size threshold larger than 10 could possibly remove some non-trivial clones from the analysis, i.e.~create more false negatives.
%On the other hand, decreasing the threshold to be lower than 10 lines will result in a larger number of clone candidate pairs to look at and a higher chance of getting false positives. Moreover, the large number of clone pairs will hinders the full manual validation of the clones and force us to rely on sampling of clone pairs. We performed a small analysis to confirm this.
%
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{../boxplot_clone_size}
%	\caption{Size of online code clones.}
%	\label{fig:boxplotclonesize}
%\end{figure}
%
%Regarding increasing the minimum clone size to more than 10 lines (e.g. 15 lines), we added an analysis of the clone size as shown in Figure \ref{fig:boxplotclonesize}. We found that the distribution of true clones; QS, SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines. Increasing the threshold to be higher than 10 would remove some of the trivial BP and IN clone pairs which are not interesting for this study. However, it will also remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
%
%Regarding decreasing the minimum clone size to be less than 10 lines, we reran the two clone detection tools (Simian and SourcererCC) again using a minimum clone size of 6 lines, another well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}. Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs using Bellon's ok-match threshold $t=0.5$. With this large amount of clone candidate pairs, it is not feasible to manually confirm all of the clones and we must rely on sampling. Moreover, it is known that lowering the number of minimum clone lines is harmful to precision. This will result in weaker findings and weaker conclusion. Thus, we decide to retain the minimum clone size of 10 lines to keep the balance between the number of non-trivial clone pairs and the feasibility of manual clone investigation.

>>>>

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software
Engineering. This is a re-submission of the previous submission
no.~TSE-2017-11-0335 and we would like to thank the anonymous reviewers for
taking their time to carefully read our paper. With their useful and
constructive reviews, we substantially improved the work by adding five major
improvements as listed below to our previous submission and minor improvements
as discussed later in this letter.

\textbf{1.~A Stack Overflow Visitor survey}~To understand the effects of toxic
code snippets on Stack Overflow to information seekers who look for coding
solutions on Stack Overflow, we performed another survey of 87 Stack Overflow
visitors. The survey shows that the visitors experienced several problems from
reusing Stack Overflow code snippets including outdated code. They are 85\% of
them that are not aware of CC BY-SA 3.0 license enforced by Stack Overflow and
66\% never check for license conflicts when reusing code snippets.

\textbf{2.~A study of toxic code snippets on GitHub:}~To provide evidence that
toxic code snippets are actually reused in software projects and to strengthen
the motivation, we performed a large-scale analysis of clones between the
discovered online code clones (100 outdated and 214 license-incompatible code
snippets) and 130,703 GitHub projects using a clone detection tool followed by
manual validation.

\textbf{3.~An analysis of the tools' parameter settings:}~We mitigated the
threats to validity due to parameter settings of the clone detection tools and
the clone merging technique by exploring different tools' parameter values. We
discovered that using the minimum clone size threshold of 10 lines gave the
highest number of non-trivial clone pairs and using the Bellon's ok-match
threshold of 0.5 gave the highest clone merging precision. We updated the
results in the paper to reflect the findings.

\textbf{4.~An extended analysis of outdated code clones:}~We performed an
extended analysis on the 100 outdated code snippets. For example, we analysed
age of the clones; studied effects of comments, newer answers, higher-voted
answers on the outdated answers; and summarised the six intents that made the
clones outdated. We found that, on average, the code is cloned to Stack Overflow
2 years after it appears in Qualitas projects, and comments/newer or
higher-voted answers did not strongly affect the outdated answers (99\% are
still marked as accepted). Lastly, we discovered that the code are outdated
because of code enhancement (65\%), followed by code deprecation (15\%), but
fixing (10\%), code refactoring (6\%), changing coding style (3\%), and data
format change (2\%).

\textbf{5.~Revisions to the overall discussion:}~We substantially expanded the
overall discussion to include (1) a discussion of toxicity of outdated and
license-incompatible clones on Stack Overflow and their implications, and (2)
more detailed discussion of how to implement the tools or approaches proposed
for preventive and detective measures, and (3) a suggestion for automation of
code cloning direction detection.

We also tried our best to address all the comments from the reviewers. Every
comment led to an improvement on this submission and we discuss them in order as
shown in the next sections.

Lastly, we would also like to ask the reviewers to comment on how to address the
newly established page limits of IEEE TSE that was enforced after our previous
submission. After incorporating the suggestions from the reviewers and
rewriting, our paper is now extended to 22 pages. Are there any elements that
could or should be removed, or should a split into two separate papers be
considered?

@@

\begin{enumerate}
	\item We understand the concern of finding real evidence to support the claim that code snippets on Stack Overflow do appear in open- or closed-source software projects. Hence, we have performed a study of code clone detection between our 100 reported outdated code snippets on Stack Overflow and 131,703 GitHub projects. We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not. We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them. As shown in Table~\ref{tab:outdated_github} below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub. For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippet and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).

@@

Interestingly, we discovered that the buggy version of the
\texttt{humanReadableInt()} method from Hadoop appears in two popular Java
projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
this method, which is exactly the same as the toxic code snippet we found on
Stack Overflow, appear in the two projects. It is possible that the developers
retrieved them from Stack Overflow, other websites, or from Hadoop code base
directly. Nevertheless, we reported them to the developers of the two projects
regarding the issue. We created a bug report for each project (deeplearning4j
\#4694\footnote{deeplearning4j bug report:
	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
HIVE-18929\footnote{Apache Hive bug report: \url{
		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
developers by describing the problem of race condition in the outdated version
of the \texttt{humanReadableInt()} method and proposed a fix by using the
newest version of the method in Hadoop. The issue has been fixed in
deeplearning4j. The developers of deeplearning4j agreed that the method was
problematic and decided to implement their own fix due to a concern of a
potential software licensing conflict caused by copying the fix directly from
the Hadoop code base. On the other hand, the bug report in Apache Hive is still
open.

	\item The same study has been done for another type of toxic code snippets on
Stack Overflow, license-incompatible code snippets. We detected clones between
the 214 code snippets without their original license (86 QS, 78 EX and 50 UD) 
and 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
In contrast to the outdated clones, we discovered many more clones of 7,207
candidate pairs. 
There were 95 pairs from 10
Qualitas projects hosted on GitHub and 7,112 pairs from 2,427 other projects.
Then, we used the Ninka tool to automatically identify
software licenses from the reported cloned snippets. Shown in
Table \ref{tab:license_github} below, the clones were found in highly-starred
projects (29,465 to 10 stars) to 1-star projects. We found 12 code snippets
with attributions to Stack Overflow questions/answers and 6 of them were the
answers we found as clones from Qualitas or external sources. Five code
snippets did not have a license while the originals had the Apache-2, GPLv2, or EPLv1
license. One snippets had the AGPLv3 license while the original had the Apache-2
license. Only 995 code snippets in GitHub projects have the same license
as the originals in Qualitas.

@@

	\item With the finding above, we show that clones of toxic Stack Overflow 
code fragments do occur in several open source software projects on GitHub.
However, we could not establish strong evidence that the toxic code snippets
were originated from Stack Overflow due to lack of supporting information.
Hence, we softened our claim by changing the statement ``\textit{It is probably
	more important than studying the effects of reusing Stack Overflow code
	snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the
	effects of reusing Stack Overflow code snippets ...}''. We also updated the
Overall Discussion section to reflect the findings that (1) there is only a
small number of toxic code snippets from outdated code that are found in GitHub
projects, (2) there is a large number of toxic code snippets caused by missing
license that are found in GitHub projects. %Moreover, the direction of copying
% is also unclear. The clones could come from Stack Overflow, the original
% project repositories, or other places.
\end{enumerate}

@@

We partially address this comment in the previous answer by performing an
empirical study of code cloning between toxic Stack Overflow code snippets and
GitHub projects. Furthermore, we also improved the paper on the aspect of the
awareness of information-seekers to toxic code snippets on Stack Overflow by
including the results from another survey of Stack Overflow visitors
(i.e.~information seekers). This survey of the Stack Overflow visitors was
performed during the same time as the Stack Overflow answerers (25 July 2017 to
25 September 2017) and the full results are reported in our technical
report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the
previous version of the paper due to a smaller sample size compared to the
answerers survey. However, we did find some interesting results so we have
included them into this version and discussed the key findings in~RQ1. The brief
summary of the visitor survey is as follows.

@@

We surveyed 87 Stack Overflow visitors (visited the site and reused code from Stack
Overflow at least once) via five channels: social media post (Facebook),
\textsf{blognone.com} (a popular IT community and discussion forum in Thailand),
the University of Molise in Italy where the third author works, the
\texttt{comp.lang.java.programmer} group and the Software Engineering Facebook
page.

The visitors survey confirms the findings from the previous studies that Stack
Overflow code snippets can be problematic~\citep{Zhang2018,Acar2016,An2017}. Sixty-six
percent of the visitors experienced a problem from reusing Stack Overflow code
snippets ranging from incorrect solutions, outdated solutions, mismatched
solutions, to buggy code. Although they are aware of the problems, half of them
(56\%) never report back to the Stack Overflow discussions. On the other hand,
the visitors rarely give attributions to Stack Overflow when they reuse code
snippets from the website, similar to the findings reported
by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
license, and more than half of them never check for license compatibility when
reusing Stack Overflow code snippets. 
Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
check if the code snippet originated from a different source (e.g.~an open source project) 
and if they had an incompatible license to their projects.
Moreover, we also found that 9\% of the participants
encountered legal issues by copying code from Stack Overflow. To the best of our
knowledge, a study of legal problems from reusing Stack Overflow code snippets
has never been done before and will be our future work.

@@

\begin{enumerate} \item We added a discussion of toxicity of outdated and
	license-incompatible clones on Stack Overflow. Although we found some harmful
	outdated clones, we could not find evidence that they are widely reused in open
	source projects on GitHub. Therefore, the damage is not high since there are only
	a few outdated code snippets that are harmful for reuse. On the other hand, the
	problem of license incompatibility caused by missing original licenses in Stack
	Overflow code snippets can cause more damage than outdated code. Different legal
	system and different interpretation of fair-use concept and de minimis (i.e.~the
	minimal lines of code allowed to be copied without violating copyright) in each
	country can make a reuse of these code snippets legally problematic.

@@

	\item To address your point about auditing platforms/services, we performed a
	study of two open source software auditing platforms/services:~BlackDuck
	Software\footnote{https://www.blackducksoftware.com} and
	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from
	their report~\cite{CORSI2017} that while they check for code copied from open
	source projects including GitHub and Stack Overflow and analyse their license
	compatibility with their customer software, the BlackDuck auditing system will
	treat the code snippets on Stack Overflow as having an ``unknown'' license because
	it does not know the original license of Stack Overflow code snippets. For
	nexB, their product does not mention checking of reused source code from Stack
	Overflow. So, our proposed preventive measure, which can offer more precise
	licensing information of Stack Overflow code snippets, will be useful as an
	add-on license check for code copying from Stack Overflow. We include this in
	the Overall Discussion. \end{enumerate}

@@

You are right. We mainly study online code clones and established their
existence. However, we used the term ``toxic code snippets'' in order to
emphasise the possible ramifications from online code cloning. Moreover, the
term code cloning is not well known outside the code cloning community. Code
clones are called differently in each research community or in practice, such as
duplicated code, copy-and-paste code, code reuse, software similarity or
software redundancy. So, we decided not to use the term in the title.

@@

``Although this activity of online code cloning is well-known, there are only a
few empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017},
especially on finding the origins of the clones. We tackle this challenge of
establishing existence of online code clones and investigate how they occur in
this study.'' %Considering your suggestion and another suggestion by Reviewer 2
% that the definition of ``toxic code snippets'' is vague, we also tightened the
% definition of toxic code snippets to be more precise.

@@

That is a fair point and we would like to analyse the statistics as you
suggested. To answer your question (a), the number of views is for the whole
Stack Overflow post but we use it as a proxy of the number of views the accepted
answer receives because the question and the answer of the two motivation
examples have a short gap of posting time (within the same day and four days
after). For (b), unfortunately, for our experiment we extracted only the code
snippets from the Stack Overflow dumps but not other information. They are the
only available data of the January 2016 snapshot we currently have. We checked
and found that the latest available Stack Overflow dump already contains
different data than the one we used in our study since it is more than 2
years newer, and will result in incorrect statistics and inconsistent results.
For (c), that is a really interesting idea. However, it is out of the scope of
this study and would involve an extensive analysis of the data so we may
investigate it in the future work.

@@

Thank you for the detailed checking of the Stack Overflow post. Interestingly,
this is surprising to us as well. The comment in the post 22262310 by Joseph K
on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare}
method is actually from a student in our class. His name is Joseph Kalash and he
is a master student in Machine Learning MsC program at UCL Computer Science
department\footnote{Joseph's CV can be found here: \url{https://jkala.sh/cv}}.
We assigned a preprint of this paper to students in the COMPGS11 -- Research
Seminar in Software Engineering course and had a discussion about the paper on
Thu 2 November 2017. Joseph, who was an active Stack Overflow member, was one of
the students in the class and he actively participated in the discussion. It
seems that he had seen the Hadoop's toxic code snippet in the paper and decided
to post a comment to warn other users.

Nevertheless, since this is a very interesting suggestion, we also performed an
investigation of the 100 answers of our reported outdated code snippets on Stack
Overflow on 6 May 2018 to see if there is any comment to mitigate or point out
the toxicity of the code snippet. We include the result of this investigation in
RQ4. We found that out of 100 answers containing outdated code snippets,
there were 6 answers that had a comment saying the code in the answer is
outdated or contains issues (including Joseph's comment). Thus, there are about
6\% of outdated answers that were notified by the Stack Overflow users based on
our analysed data. None of the 6 answers change their outdated code, but the
comments themselves may help to warn other Stack Overflow users. We added this
discussion to RQ4.

@@

We appreciate the comments. We have refined our definition of toxic code
snippets in the paper by adapting Israel Gat's definition~\citep{toxiccode}
which links toxic code to technical debt, i.e.~``a metaphor reflecting technical
compromises that can yield short-term benefit but may hurt the long-term health
of a software system''~\citep{Li2015}. The new definition of toxic doe snippets
are as follows.

@@

Stack Overflow allows its users to edit their own posts,
i.e.~questions/answers\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts\footnote{https://stackoverflow.com/help/privileges/edit}. Thus, if the code snippet in an answer is outdated and has an issue, the answerer or other high-reputation users can update the answer to be up-to-date or to warn other users that the code is already outdated and may contain problems. We found some discussions regarding this concern on Metaexchange as well so the Stack Overflow community is also considering this option\footnote{Discussion about outdated answer: https://meta.stackexchange.com/questions/131495/how-to-handle-outdated-answers and https://meta.stackexchange.com/questions/180864/editing-outdated-source-code-in-an-answer}. We included this discussion in the paper.

Based on your suggestion of looking at other newer or higher-voted answers, we
performed an investigation of all the answers in 100 posts containing outdated
code snippets as accepted answers. We found that there were 34 posts which
contains newer answers. Regarding the number of votes, there were 5 posts which
contained other answers with a higher number of votes than the outdated answer.
Ninety-nine out of the one hundred outdated code snippets were still marked as accepted
answers. This discussion of the findings is added to RQ4.

@@

Good point. Although we grouped the code modifications that make Stack Overflow
snippets outdated into 6 categories as shown in Table 9, we did not investigate
the motivation of the changes such as code refactoring or variable renaming. We
have performed the check as you suggested by checking the commit message of each
change that make the code outdated. The findings are discussed below and are
included in RQ4.

@@

The majority (64) of the changes are due to code enhancement, such as adding a
new features or improving existing code to support a newer version of the
language or APIs. Fifteen changes are for removal of dead or deprecated code
such as the SQL connection code example in Hibernate. Ten changes are made to
fix bugs in the software (e.g.~array reference, race condition, wrong field
access, \texttt{NullPointerException}). There are 6 changes for code
refactoring, 3 changes for updating coding styles using an automated tool or
manually, and 2 changes that are caused by the change of data format.

@@

We used the Stack Overflow data dump of January 2016 since it was the latest
dump when we started our experiment. We completed the whole
experiment, the result analysis, and the survey two years later. That is why the
dump is 2 years old.

@@

%Choosing this size threshold larger than 10 could possibly remove some
% non-trivial clones from the analysis, i.e.~create more false negatives.
%On the other hand, decreasing the threshold to be lower than 10 lines will
% result in a larger number of clone candidate pairs to look at and a higher
% chance of getting false positives. Moreover, the large number of clone pairs
% will hinders the full manual validation of the clones and force us to rely on
% sampling of clone pairs. We performed a small analysis to confirm this.
%
%\begin{figure}[H]
%	\centering
%	\includegraphics[width=0.5\linewidth]{../boxplot_clone_size}
%	\caption{Size of online code clones.}
%	\label{fig:boxplotclonesize}
%\end{figure}
%
%Regarding increasing the minimum clone size to more than 10 lines (e.g. 15
% lines), we added an analysis of the clone size as shown in Figure
% \ref{fig:boxplotclonesize}. We found that the distribution of true clones; QS,
% SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines.
% Increasing the threshold to be higher than 10 would remove some of the trivial
% BP and IN clone pairs which are not interesting for this study. However, it
% will also remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
%
%Regarding decreasing the minimum clone size to be less than 10 lines, we reran
% the two clone detection tools (Simian and SourcererCC) again using a minimum
% clone size of 6 lines, another well-accepted minimum clone size in clone
% benchmark~\citep{Bellon2007}. Simian reported 67,172 clone candidate pairs and
% SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs
% using Bellon's ok-match threshold $t=0.5$. With this large amount of clone
% candidate pairs, it is not feasible to manually confirm all of the clones and
% we must rely on sampling. Moreover, it is known that lowering the number of
% minimum clone lines is harmful to precision. This will result in weaker
% findings and weaker conclusion. Thus, we decide to retain the minimum clone
% size of 10 lines to keep the balance between the number of non-trivial clone
% pairs and the feasibility of manual clone investigation.

To measure the impact of this minimum clone size threshold on the clone results,
we performed an investigation of three different threshold values: six, ten, and
fifteen lines. We started our investigation by using a threshold value of six
lines, a well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
clone candidate pairs. We randomly sampled 382 pairs from the two sets for
manual check. This sample number was a statistical significant sample with a
95\% confidence level and $\pm 5\%$ confidence interval. The first author
investigated the sampled clone pairs and classified them into three groups:
non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
setter methods), and non-trivial clones. The manual check found 26 non-clone
pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we
increased the threshold to ten lines, another well-established minimum clone
size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs
from Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and
manually checked the same amount of 382 pairs and found 27 non-clone pairs, 253
trivial clone pairs and 102 non-trivial clone pairs. Then, we increased the
threshold further to fifteen lines and retrieved 196 clone pairs from Simian and
1,230 clone pairs from SourcererCC. The manual check of the 382 randomly sampled
pairs reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial
clone pairs.
